An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems

### 2014-04-28 paper/paper.tex
Paper: Minor modifications to the paper

% highlights of methodology
In order to determine whether or not our system provides solutions for the challenges of both P2P and centralized backup systems, we created test scenarios that test how well our system handles these challenges. We first tested how BitTorrent Sync handles a varying number of files to backup by backing up 1 GB of data split up into one 1GB file, ten 100MB files, and one hundred 10MB files, and measuring the rates of data transfer over time. This was done on a network with just enough peers to have one file backed up with sufficient replication.

@@

% key results and conclusions
After running our tests, we found that BTBackup, and by extension BitTorrent, performs well as the data layer transport protocol for a P2P backup system. Specifically, we found that larger but fewer files are handled more efficiently than a greater number of smaller files, given the same amount of total data. We also determined that our system handles node churn well, when the rate of churn is modeled off of the average Internet user. Our final and most important result is that our system was able to achieve data transfer rates that are quicker than the rates that could be realistically achieved if the file transfers occurred between the peer and one other entity, which would be a central entity in a centralized backup system or one other peer in other P2P backup systems. This means that we can confidently conclude that BitTorrent is an excellent choice for the data transfer protocol in P2P backup systems.

>>>>

% highlights of methodology
In order to determine whether or not our system provides solutions for the challenges of both P2P and centralized backup systems, we created test scenarios that test how well our system handles these challenges. We first tested how BitTorrent Sync handles a varying number of files to backup by backing up 1 GB of data split up into one 1 GB file, ten 100 MB files, and one hundred 10 MB files, and measuring the rates of data transfer over time. This was done on a network with just enough peers to have one file backed up with sufficient replication.

@@

% key results and conclusions
After running our tests, we found that BitTorrent performs well as the data layer transport protocol for a P2P backup system. Specifically, we found that larger but fewer files are handled more efficiently than a greater number of smaller files, given the same amount of total data. We also determined that our system handles node churn well, when the rate of churn is modeled off of the average Internet user. Our final and most important result is that our system was able to achieve data transfer rates that are quicker than the rates that could be realistically achieved if the file transfers occurred between the peer and one other entity, which would be a central entity in a centralized backup system or one other peer in other P2P backup systems.
